RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-01-29 assets/illustration/time_structure.tex
:lipstick: Update illustrations

\begin{tikzpicture}[font=\large]
	% BC/AmBC/SR
	\foreach \x in {0,...,3}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,7}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
		}

	% RIScatter
	\foreach \x in {0,...,1}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {2,...,7}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}

	\foreach \x in {1,...,7}{
			% \draw[dotted] (\x,1) -- (\x,3.75);
			\draw[dotted] (\x,1) -- (\x,3.25);
		}
	\draw[latex-latex] (0,1.4) -- (0.5,1.4) node[above,midway,yshift=1]{PB};
	% \draw[latex-latex] (0,4.1) -- (1,4.1) node[above,midway,yshift=1]{BB};
	\draw[latex-latex] (0,2.4) -- (1,2.4) node[above,midway,yshift=1]{BB};
	\draw[latex-latex] (0,3.4) -- (8,3.4) node[above,midway,yshift=1]{Channel Block};

	\node at (-2,3.125) {BackCom};
	\node at (-2,2.125) {RIS};
	\node at (-2,1.125) {RIScatter};

	\draw [pattern=north west lines](0.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
	\draw [pattern=north east lines](2.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
	\draw [pattern=vertical lines](4.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
	\draw [pattern=horizontal lines](6.15,0) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\small]
	% MBC/BBC
	\foreach \x in {0}{
			\draw[blue,ultra thick,postaction={pattern=north west lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\foreach \x in {1}{
			\draw[blue,ultra thick,postaction={pattern=north east lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\foreach \x in {2}{
			\draw[blue,ultra thick,postaction={pattern=vertical lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\foreach \x in {3}{
			\draw[blue,ultra thick,postaction={pattern=horizontal lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\draw[latex-latex] (0,4.35) -- (2,4.35) node[above,midway]{BB};
	\node at (-1.5,4.125) {MBC/BBC};

	% AmBC/SR
	\foreach \x in {0,...,7}{
			\draw[teal,fill=teal!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,15}{
			\draw[teal,fill=teal!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,1}{
			\draw[teal,ultra thick] (4*\x,3) rectangle ++(4,0.25);
		}
	\draw[latex-latex] (0,3.35) -- (4,3.35) node[above,midway]{BB};
	\draw[latex-latex] (0,2.9) -- (0.5,2.9) node[below,midway]{PB};
	\node at (-1.5,3.125) {AmBC/SR};

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
		}
	\draw[red,ultra thick] (0,2) rectangle ++(8,0.25);
	\draw[latex-latex] (0,2.35) -- (8,2.35) node[above,midway]{CB};
	\draw[latex-latex] (0,1.9) -- (0.5,1.9) node[below,midway]{PB};
	\node at (-1.5,2.125) {RIS};

	% RIScatter
	\foreach \x in {0,...,7,12,13,...,15}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,3}{
			\draw[brown,ultra thick] (2*\x,1) rectangle ++(2,0.25);
		}
	\draw[latex-latex] (0,1.35) -- (2,1.35) node[above,midway]{BB};
	\draw[latex-latex] (0,0.9) -- (0.5,0.9) node[below,midway]{PB};

	\node at (-1.5,1.125) {RIScatter};

	\draw [pattern=north west lines,ultra thick](0.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
	\draw [pattern=north east lines,ultra thick](2.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
	\draw [pattern=vertical lines,ultra thick](4.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
	\draw [pattern=horizontal lines,ultra thick](6.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
\end{tikzpicture}

### 2023-01-29 jsac.tex
:lipstick: Update illustrations

\begin{section}{Introduction}
	% \begin{subsection}{Fundamentals}
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
	As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
	However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
	To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
	As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
	Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
	The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
	In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
	Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
	\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
	In summary, \gls{mbc}/\gls{bbc} (resp. \gls{ris}) involves a \emph{single} passive backscatter (resp. active primary) link where the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal).
	On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
	In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
	In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
	A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.

@@

\begin{section}{RIScatter}
	% \begin{subsection}{Concepts}
	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
	RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
	Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
	It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fg:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fg:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fg:scatter_model}
		}
		\caption{
		Block diagram, equivalent circuit, and scatter model of a RIScatter node.
		The solid and dashed vectors represent signal and energy flows.
		The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
		}
		\label{fg:riscatter_node}
	\end{figure*}
	Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
	\begin{figure}[!t]
		\centering
		\subfloat[Reflection State Distribution]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/input_distribution.tex}
			}
			\label{fg:input_distribution}
		}
		\subfloat[Reflection Pattern]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/time_structure.tex}
			}
			\label{fg:time_structure}
		}
		\caption{
			Reflection state distribution and reflection pattern over time of \gls{bc}, \gls{ris}, and RIScatter.
			``PB'' means primary block and ``BB'' means backscatter block.
			Spreading factor is 2 in this example.
		}
		\label{fg:scatter_comparison}
	\end{figure}
	Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
	Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
	Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
	For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
	For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

>>>>

\begin{section}{Introduction}
	% \begin{subsection}{Fundamentals}
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
	As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
	However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
	To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
	As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
	Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
	The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
	In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
	Those \gls{bc} applications\footnote{In this paper, \gls{bc} refers to \gls{mbc}, \gls{bbc}, \gls{ambc} and \gls{sr}.} employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
	\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
	In summary, \gls{mbc}/\gls{bbc} (resp. \gls{ris}) involves a \emph{single} passive backscatter (resp. active primary) link where the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal).
	On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
	In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
	In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
	A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.

@@

\begin{section}{RIScatter}
	% \begin{subsection}{Concepts}
	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
	RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
	Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
	It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fg:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fg:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fg:scatter_model}
		}
		\caption{
		Block diagram, equivalent circuit, and scatter model of a RIScatter node.
		The solid and dashed vectors represent signal and energy flows.
		The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
		}
		\label{fg:riscatter_node}
	\end{figure*}
	Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
	\begin{figure}[!t]
		\centering
		\subfloat[Reflection State Distribution]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/input_distribution.tex}
			}
			\label{fg:input_distribution}
		}
		\subfloat[Reflection Pattern]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/time_structure.tex}
			}
			\label{fg:time_structure}
		}
		\caption{
			Reflection state distribution and reflection pattern over time of scattering applications.
			``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
			\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
		}
		\label{fg:scatter_comparison}
	\end{figure}
	Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
	Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
	Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
	For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
	For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

### 2023-01-29 main.tex
:lipstick: Update illustrations

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
		Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
		The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
		On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
		In summary, \gls{mbc}/\gls{bbc} (resp. \gls{ris}) involves a \emph{single} passive backscatter (resp. active primary) link where the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal).
		On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
		A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.

@@

\begin{section}{RIScatter}
	\begin{subsection}{Concepts}
		We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
		Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
		\begin{figure}[!t]
			\centering
			\subfloat[Reflection State Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Reflection state distribution and reflection pattern over time of \gls{bc}, \gls{ris}, and RIScatter.
				``PB'' means primary block and ``BB'' means backscatter block.
				Spreading factor is 2 in this example.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
		Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
		For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

>>>>

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, and the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig.~\subref*{fg:mbc} and \gls{bbc} in Fig.~\subref*{fg:bbc}.
		Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig.~\subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum for \gls{bc}, but the decoding is subject to a strong interference from the primary (legacy) link.
		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, and the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
		The concept was further refined by \cite{Liang2020} as \gls{sr} in Fig.~\subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly, individually, or sequentially decodes both links.
		Those \gls{bc} applications\footnote{In this paper, \gls{bc} refers to \gls{mbc}, \gls{bbc}, \gls{ambc} and \gls{sr}.} employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
		On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and adaptively optimized based on \gls{csi}.
		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
		In summary, \gls{mbc}/\gls{bbc} (resp. \gls{ris}) involves a \emph{single} passive backscatter (resp. active primary) link where the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal).
		On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency) of the primary link, while the primary link may be completely unaware of the backscatter link.
		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
		A comparison of scattering applications is summarized in Table~\ref{tb:scattering_applications}.

@@

\begin{section}{RIScatter}
	\begin{subsection}{Concepts}
		We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
		Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
		\begin{figure}[!t]
			\centering
			\subfloat[Reflection State Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Reflection state distribution and reflection pattern over time of scattering applications.
				``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
				\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
		Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
		For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
